Between-dataset comparisons

### 2019-11-15 analysis/reports/cross_dataset.Rmd
add range plots

>>>>

Looking at range of skewness and Simpsons:

```{r ranges}

skew_range_hist <- ggplot(data = filter(all_di, nsamples > 2000), aes(x = skew_range, y = skew_percentile, color = dat)) +
  geom_point(alpha = .2) +
  geom_smooth(method = "lm", se =F) +
  theme_bw() +
  scale_color_viridis_d(end = .8) +
  facet_wrap(vars(dat), scales = "free") + 
  ggtitle("Skewness")

skew_range_hist

simpson_range_hist <- ggplot(data = filter(all_di, nsamples > 2000), aes(x = simpson_range, y = simpson_percentile, color = dat)) +
  geom_point(alpha = .2) +
    geom_smooth(method = "lm", se =F) +

  theme_bw() +
  scale_color_viridis_d(end = .8) +
  facet_wrap(vars(dat), scales = "free") +
  ggtitle("Simpson")

simpson_range_hist

I added the ranges because I thought the percentiles might be constrained somewhat by the range of values represented in the feasible set. It doesn't look to me like there is a strong relationship between range and %ile.
